Beyond Simple Features: A Large-Scale Feature Search Approach to Unconstrained Face Recognition

### 2011-06-30 results.tex
Initial commit

\begin{figure*}[ht]
\centering 
\subfigure[\small{within-model-class blends}]{
  \includegraphics[scale=0.9]{figures/within_roc.pdf}
  \label{fig:within_rocs}
} 
\subfigure[\small{across-model-class blends}]{
  \includegraphics[scale=0.9]{figures/mega_blend_roc.pdf}
  \label{fig:megablend_rocs}
}
\subfigure[\small{comparison with literature}]{
    \begin{tabular}{|c||c|c|c|c|}
\hline
%Reference & Kumar et al. ICCV09 \cite{kumar:iccv09} & Wolf et al. ACCV09 \cite{wolf:accv09} & Cao et al. CVPR10 \cite{cao2010face} & This paper \\
 & Kumar et al. & Wolf et al. & Cao et al. & \\
Reference & ICCV09 \cite{kumar:iccv09} & ACCV09 \cite{wolf:accv09} & CVPR10 \cite{cao2010face} & This paper\\
\hline\hline 
Mean classification error & 14.7\%$\pm$1.2 & 13.2\%$\pm$0.3 & 15.5\%$\pm$0.5 & \bf{11.9\%$\pm$0.6} \\
\hline 
%\rule{0pt}{2ex}
\end{tabular}
\label{fig:table_soa}
}

@@

>>>>

\begin{figure*}[ht]
\centering 
\subfigure[\small{within-model-class blends}]{
  \includegraphics[scale=0.9]{figures/within_roc.pdf}
  \label{fig:within_rocs}
} 
\subfigure[\small{across-model-class blends}]{
  \includegraphics[scale=0.9]{figures/mega_blend_roc.pdf}
  \label{fig:megablend_rocs}
}
\subfigure[\small{comparison with literature}]{
    \begin{tabular}{|c||c|c|c|c|}
\hline
%Reference & Kumar et al. ICCV09 \cite{kumar:iccv09} & Wolf et al. ACCV09 \cite{wolf:accv09} & Cao et al. CVPR10 \cite{cao2010face} & This paper \\
 & Kumar et al. & Wolf et al. & Cao et al. & \\
Reference & ICCV09 \cite{kumar:iccv09} & ACCV09 \cite{wolf:accv09} & CVPR10 \cite{cao2010face} & This paper\\
\hline\hline
Mean classification error & 14.7\%$\pm$1.2 & 13.2\%$\pm$0.3 & 15.5\%$\pm$0.5 & \bf{11.9\%$\pm$0.6} \\
\hline
\end{tabular}
\label{fig:table_soa}
}

@@

\subsection{Analysis of Tolerance to Variation, Using Synthetic Faces}

% -------------------------------------
%  Variation level figure
% -------------------------------------

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.8]{figures/eight_faces_naturalbg_variation_v1like_a_plus.pdf}
    \caption[]{{\bf Model performance on synthetic faces as a function of level of variation}}
	\label{fig:perf_variation_levels}
\end{figure}

\subsubsection{Performance as a function of variation level}

The synthetic face evaluation sets used here provide us with the ability to parametrically control the level of rotation, position and scale variation that our models are required to tolerate.  Figure \ref{fig:perf_variation_levels} shows the performance the best models from each model class (V1-like, HT-L2, HT-L3) as a function of (composite) variation level for an eight-way face classification task.

\subsubsection{Effect of number of faces to be discriminated}

To further explore the behavior of our models with a controlled stimulus, we examined model
performance as a function of the number of faces to be discriminated.  In particular, we
considered cases with two, four, six, and eight faces.  Performance, grouped by model is shown
in Figure \ref{fig:nfaces_by_model}, and is shown grouped by variation level in 
Figure \ref{fig:nfaces_by_variation}.  Predictably, absolute performance level is depressed as a larger
number of faces is considered, as is the chance performance level (dotted line). Interestingly, the
rate at which performance falls off varies between models as a function of both number of faces
to be discriminated, and as a function of variation level.  The stability of the performance of the 
largest/deepest model --- HT-L3-1st --- is most pronounced when large number of faces and large amounts of variation 
are considered.  Differences between models are far less pronounced with smaller numbers of
faces and lesser degrees of variation.

% -------------------------------------
%  N Faces Figure 2
% -------------------------------------

\begin{figure*}[ht!]
\centering 
\subfigure[\small{V1-like}]{
  \includegraphics[scale=0.65]{figures/nfaces_variation_NaturalBg_v1like_a_plus.pdf}
  \label{fig:nfaces_v1like}
} 
\subfigure[\small{HT-L2-1st}]{
  \includegraphics[scale=0.65]{figures/nfaces_variation_NaturalBg_ht1_1_l2_1st.pdf}
  \label{fig:nfaces_l2}
} 
\subfigure[\small{HT-L3-1st}]{
  \includegraphics[scale=0.65]{figures/nfaces_variation_NaturalBg_ht1_1_l3_1st.pdf}
  \label{fig:nfaces_l3}
}
\caption[]{{\bf Effect of number of synthetic faces to be discriminated, sorted by model}}
\label{fig:nfaces_by_model}
\end{figure*}

% -------------------------------------
%  N Faces Figure
% -------------------------------------

\begin{figure*}[ht]
\centering 
% \subfigure[\small{no variation}]{
%   \includegraphics[scale=0.6]{figures/nfaces_variation0_by_model.pdf}
%   \label{fig:nfaces_var0}
% } 
\subfigure[\small{variation level 2}]{
  \includegraphics[scale=0.7]{figures/nfaces_variation2_by_model.pdf}
  \label{fig:nfaces_var2}
} 
\subfigure[\small{variation level 4}]{
  \includegraphics[scale=0.7]{figures/nfaces_variation4_by_model.pdf}
  \label{fig:nfaces_var4}
}
\subfigure[\small{variation level 6}]{
  \includegraphics[scale=0.7]{figures/nfaces_variation6_by_model.pdf}
  \label{fig:nfaces_var6}
}

\caption[]{{\bf Effect of number of synthetic faces to be discriminated, sorted by variation level.} Note that the performance was 100\% in all cases for the zero variation condition (data not shown).}
\label{fig:nfaces_by_variation}
\end{figure*}

\subsubsection{Effect of background}

To explore the role of background variation, we evaluated model performance with four different background conditions: no background, white-noise background, phase-scrambled natural backgrounds (i.e. approx. 1/f noise), and natural backgrounds.  Performance as a function of background and variation level is shown Figure \ref{fig:perf_bg_variation}.  Choice of background was found to have a profound effect on model performance.  In the absence of a background, the performance for most models remained high, even at relatively high levels of variation in view, position, and scale (e.g. greater than 90\% performance at variation level 4 for the HT-L3-1st and V1-like models).  However, the inclusion of any background resulted in a precipitous drop-off in performance for all models, except for the HT-L3-1st model, whose performance degraded gradually.  In general, progressively more realistic backgrounds proved increasingly difficult for all models.

% -------------------------------------
%  Effect of Background Figure
% -------------------------------------

\begin{figure*}[ht]
\centering 
% \subfigure[\small{no variation}]{
%   \includegraphics[scale=0.45]{figures/bg_variation0_by_model.pdf}
%   \label{fig:bg_var0}
% } 
\subfigure[\small{variation level 2}]{
  \includegraphics[scale=0.55]{figures/bg_variation2_by_model.pdf}
  \label{fig:bg_var2}
} 
\subfigure[\small{variation level 4}]{
  \includegraphics[scale=0.55]{figures/bg_variation4_by_model.pdf}
  \label{fig:bg_var4}
}
\subfigure[\small{variation level 6}]{
  \includegraphics[scale=0.55]{figures/bg_variation6_by_model.pdf}
  \label{fig:bg_var6}
}

\caption[]{{\bf Effect of background type on performance with synthetic faces.} Note that the performance was 100\% in all cases for the zero variation condition (data not shown).}
\label{fig:perf_bg_variation}
\end{figure*}
